Abstract

### 2025-10-02 output/Main_text.Rmd
Add contours to item plots
Reorder also the plots in the order in which they are used.
Output plot with contour plots in manuscript

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     3.1
#| fig.width:      6.65
plot_orth + plot_oblique

>>>>

```{r density-contours}
```

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     3
#| fig.width:      6.65
#| warning:        false
plot_orth_uncorr_contours + plot_oblique
